Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-18 papers/clusters.tex
Define 'on'

One final note:
we think of this \documentname\ as performing a proof of concept.
We know that the stellar members of open and globular clusters---stars
that are identified by being close in phase space---contain highly
informative abundance information that identifies them also in
chemical-abundance space.
Does this work the other way around? I.e. can chemical tagging identify small subsets of stars, among a vastly greater background sample, that have a common birth origin. If we find stars purely by their clustering in abundance space and subsequently show that they are part of a still spatially coherent cluster, then chemical tagging is
\emph{on.}

>>>>

One final note:
we think of this \documentname\ as performing a proof of concept.
We know that the stellar members of open and globular clusters---stars
that are identified by being close in phase space---contain highly
informative abundance information that identifies them also in
chemical-abundance space.  Does this work the other way around? 
Can chemical tagging identify small subsets of stars, among a vastly
greater background sample, that have a common birth origin? If we 
find stars purely by their clustering in abundance space and subsequently
show that they are part of a still spatially coherent cluster, then
we will have resolved all practical outstanding issues plaguing 
chemical tagging, thereby enabling tantalizing potential to truly
unravel the formation of the Milky Way.
